Notes: New gaugings in 3d from three-form

### 2023-05-08 Notes_3dH3.tex
Draft created by Emanuel.

  From these decompositions we extract the relations between the charges:
  \begin{equation}
    \begin{cases}
    q_{\SL(6)} = -\dfrac{1}{2}(q_{\SL(3)_{1}}+q_{\SL(3)_{2}}), \\[7pt]
    q_{\SL(2)_{\rm IIB}} = \dfrac{1}{4}\,\left(q_{\SL(3)_{1}}-q_{\SL(3)_{2}}+q_{\SL(8)}\right), \\[7pt]
    q_{\rm IIB} = \dfrac{1}{2}\,\left(-q_{\SL(3)_{1}}+q_{\SL(3)_{2}}+3\,q_{\SL(8)}\right).
    \end{cases}
  \end{equation}
  So the coordinates are inside $(\bm{6},\bm{1})_{-2}\oplus(\bm{1},\bm{6})_{2}$ of $\SL(4)_{1}\times\SL(4)_{2}\times\R^{+}_{\SL(8)}$. \ce{Problem with $3, \bar{3}$? Comes from identification $\bm{6'}=\bm{\bar{6}}$?}

@@

  \subsubsection{Deformation \texorpdfstring{${\cal V}^{(+)}$}{V+}}
  Study of deformation with ${\cal V}^{(+)}$ with half-maximal theory (access to full spectrum). For $\zeta^{2}_{+}=1-e^{-2\omega_{+}}$, $D^{1}(2,1;\alpha)_{\rm L}$ broken, for even part:
  \begin{equation}
    \SL(2,\mathbb{R})_{\rm L}\times\SO(3)^{+}_{\rm L}\times\SO(3)^{-}_{\rm L} \longrightarrow \SL(2,\mathbb{R})_{\rm L}\times\SO(2)^{+}_{\rm L}\times\SO(3)^{-}_{\rm L}
  \end{equation}
  Then spectrum organized in terms of lon multiplet of $D^{1}(2,1;\alpha)_{\rm R}$, charge $q_{\rm L}^{+}$ and spin $j_{\rm L}^{+}$:
  \begin{equation}
    \left[\ell^{+}_{R},\ell^{-}_{R}\right]^{j_{\rm L}^{+}}_{_{\rm L}^{+}},
  \end{equation}
  with conformal weight:
  \begin{equation}
    \Delta_{q}^{\ell^{+},\ell^{-}} = -\frac{1}{2} + \frac{1}{2}\sqrt{1+\frac{4\ell^{+}(\ell^{+}+1)+q^{2}(e^{2\omega}-1)+4\alpha^{2}\ell^{-}(\ell^{-}+1)}{1+\alpha^{2}}}.
  \end{equation}
  For ${\cal V}^{(-)}$, $\alpha\rightarrow\alpha^{-1}$.

@@

\paragraph{\boldmath $H_{(3)}$ and $*H_{(3)}$ in the embedding tensor} The embedding tensor of the $\SO(4,4)$ exceptional theory has two different components: $\theta_{[MNPQ]}\subset\bm{35_{\rm s}}\oplus\bm{35_{\rm c}}$ and $\theta_{(MN)}\subset\bm{35_{\rm v}}$. It decomposes as follows under $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}$:
\begin{equation}
  \begin{aligned}
    \bm{35_{\rm v}} &\longrightarrow \bm{1}_{4} \oplus {\color{mydarkorange}\bm{6}_{2}} \oplus \bm{1}_{0} \oplus \bm{20'}_{0} \oplus \bm{6}_{-2} \oplus \bm{1}_{-4},\\
    \bm{35_{\rm s}} &\longrightarrow {\color{mydarkorange}\bm{10}_{2}} \oplus \bm{15}_{0}  \oplus \bm{\bar{10}}_{-2},\\
    \bm{35_{\rm c}} &\longrightarrow {\color{mydarkorange}\bm{\bar{10}}_{2}} \oplus \bm{15}_{0}  \oplus \bm{10}_{-2},
  \end{aligned}
\end{equation}
where the colored representations are those coming from the three-forms. Only $\bm{10}_{2}$ and $\bm{\bar{10}}_{2}$ feature $\SO(4)$ singlets. \ce{So no distinction between (1,1) and (2,0)? Because triality, or I made errors?} $\leq$

>>>>

  From these decompositions we extract the relations between the charges:
  \begin{equation}
    \begin{cases}
    q_{\SL(6)} = -\dfrac{1}{2}(q_{\SL(3)_{1}}+q_{\SL(3)_{2}}), \\[7pt]
    q_{\SL(2)_{\rm IIB}} = \dfrac{1}{4}\,\left(q_{\SL(3)_{1}}-q_{\SL(3)_{2}}+q_{\SL(8)}\right), \\[7pt]
    q_{\rm IIB} = \dfrac{1}{2}\,\left(-q_{\SL(3)_{1}}+q_{\SL(3)_{2}}+3\,q_{\SL(8)}\right).
    \end{cases}
  \end{equation}
  So the coordinates are inside $(\bm{6},\bm{1})_{-2}\oplus(\bm{1},\bm{6})_{-2}$ of $\SL(4)_{1}\times\SL(4)_{2}\times\R^{+}_{\SL(8)}$. \ce{Problem with $3, \bar{3}$? Comes from identification $\bm{6'}=\bm{\bar{6}}$?}

@@

  \subsubsection{Deformation \texorpdfstring{${\cal V}^{(+)}$}{V+}}
  Study of deformation with ${\cal V}^{(+)}$ with half-maximal theory (access to full spectrum). For $\zeta^{2}_{+}=1-e^{-2\omega_{+}}$, $D^{1}(2,1;\alpha)_{\rm L}$ broken, for even part:
  \begin{equation}
    \SL(2,\mathbb{R})_{\rm L}\times\SO(3)^{+}_{\rm L}\times\SO(3)^{-}_{\rm L} \longrightarrow \SL(2,\mathbb{R})_{\rm L}\times\SO(2)^{+}_{\rm L}\times\SO(3)^{-}_{\rm L}
  \end{equation}
  Then spectrum organized in terms of lon multiplet of $D^{1}(2,1;\alpha)_{\rm R}$, charge $q_{\rm L}^{+}$ and spin $j_{\rm L}^{+}$:
  \begin{equation}
    \left[\ell^{+}_{R},\ell^{-}_{R}\right]^{j_{\rm L}^{+}}_{q_{\rm L}^{+}},
  \end{equation}
  with conformal weight:
  \begin{equation}
    \Delta_{q}^{\ell^{+},\ell^{-}} = -\frac{1}{2} + \frac{1}{2}\sqrt{1+\frac{4\ell^{+}(\ell^{+}+1)+q^{2}(e^{2\omega}-1)+4\alpha^{2}\ell^{-}(\ell^{-}+1)}{1+\alpha^{2}}}.
  \end{equation}
  For ${\cal V}^{(-)}$, $\alpha\rightarrow\alpha^{-1}$.

@@

\paragraph{\boldmath $H_{(3)}$ and $*H_{(3)}$ in the embedding tensor} The embedding tensor of the $\SO(4,4)$ exceptional theory has two different components: $\theta_{[MNPQ]}\subset\bm{35_{\rm s}}\oplus\bm{35_{\rm c}}$ and $\theta_{(MN)}\subset\bm{35_{\rm v}}$. It decomposes as follows under $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}$:
\begin{equation}
  \begin{aligned}
    \bm{35_{\rm v}} &\longrightarrow \bm{1}_{4} \oplus {\color{mydarkorange}\bm{6}_{2}} \oplus \bm{1}_{0} \oplus \bm{20'}_{0} \oplus \bm{6}_{-2} \oplus \bm{1}_{-4},\\
    \bm{35_{\rm s}} &\longrightarrow {\color{mydarkorange}\bm{10}_{2}} \oplus \bm{15}_{0}  \oplus \bm{\bar{10}}_{-2},\\
    \bm{35_{\rm c}} &\longrightarrow {\color{mydarkorange}\bm{\bar{10}}_{2}} \oplus \bm{15}_{0}  \oplus \bm{10}_{-2},
  \end{aligned}
\end{equation}
where the colored representations are those coming from the three-forms. Only $\bm{10}_{2}$ and $\bm{\bar{10}}_{2}$ feature $\SO(4)$ singlets. \ce{So no distinction between (1,1) and (2,0)? Because triality, or I made errors?}

\section{\texorpdfstring{$\E_{8(8)}$}{E8(8)} identities}

\begin{gather}
  \eta^{MN} = \frac{1}{60}\,f^{MK}{}_{L}f^{NL}{}_{K}, \\
  \M^{PM}\M^{QN}f_{PQ}{}^{K} = - f^{MN}{}_{L}\M^{LK}, \\
  J_{\bar M\bar N}{}^{\bar P} = U_{\bar M}{}^{M}\partial_{M}U_{\bar N}{}^{P}U^{\bar P}{}_{P}, \\
  f^{K}{}_{MR}f^{RL}{}_{N}\,J_{KP}{}^{Q}J_{LU}{}^{V} = J_{MP}{}^{Q}J_{NU}{}^{V}+J_{NP}{}^{Q}J_{MU}{}^{V},\\
  f^{MN}{}_{P}J_{KL}{}^{P} = -2\,J_{KP}{}^{[M}f^{N]P}{}_{L}, \\
  J_{MN}{}^{P} = \frac{1}{60} \,f_{N}{}^{PR}f_{RK}{}^{L}J_{ML}{}^{K}, \\
  J_{MN}{}^{P} = -\frac{1}{30} \,f_{N}{}^{KR}f_{R}{}^{P}{}_{L}J_{MK}{}^{L},\\
  f_{M}{}^{KL}J_{KL}{}^{R}J_{RP}{}^{Q} = f_{M}{}^{KL}J_{RQ}{}^{P}J_{KL}{}^{K},\\
  2\,J_{L[M}{}^{K}f_{N]K}{}^{L} = -f_{MN}{}^{K}J_{LK}{}^{L}.
\end{gather}

Section constraint (one of them):
\begin{equation}
  f^{K}{}_{MR}f^{RL}{}_{N} \,\partial_{K}\otimes\partial_{L} = 2\,\partial_{(M}\otimes\partial_{N)}.
\end{equation}
